FITS format for planetary surfaces: definitions, applications and best practices.

### 2017-08-25 epss_marmo.tex
Update on Overleaf.

% Now, type in the journal name: \journalname{<Journal Name>}
% ie,
\journalname{JGR-Atmospheres}

@@

\title{Trends in the predictive performance of raw ensemble weather forecasts}

@@

 \authors{A. B. Smith\affil{1}\thanks{Current address, McMurdo Station,
 Antartica},
 Eric Brown\affil{1,2}, Rick Williams\affil{3},
 John B. McDougall\affil{4}, and S. Visconti\affil{5}\thanks{Also
 funded by Monsanto.}}

\affiliation{1}{Department of Hydrology and Water Resources,
University of Arizona, Tucson, Arizona, USA.}
\affiliation{2}{Department of Geography, Ohio State University,
Columbus, Ohio, USA.}
\affiliation{3}{Department of Space Sciences, University of
Michigan, Ann Arbor, Michigan, USA.}
\affiliation{4}{Division of Hydrologic Sciences, Desert Research
Institute, Reno, Nevada, USA.}
\affiliation{5}{Dipartimento di Idraulica, Trasporti ed
Infrastrutture Civili, Politecnico di Torino, Turin, Italy.}

@@

\correspondingauthor{A. B. Smith}{email@address.edu}

@@

\begin{keypoints}
\item Evolution of raw ensemble forecast \replaced{skill}{skills}
\item Future benefits from statistical post-processing
\item Global distribution of forecast skill development
\end{keypoints}

>>>>

% Now, type in the journal name: \journalname{<Journal Name>}
% ie,
\journalname{Earth and Space Science}

@@

\title{FITS format for planetary surfaces: definitions, applications and best practices.}

@@

 \authors{C. Marmo\affil{1},
 T. M. Hare\affil{2}, ...}

\affiliation{1}{GEOPS, Univ. Paris-Sud, CNRS, Univ. Paris-Saclay, Orsay, France}
\affiliation{2}{U. S. Geological Survey, Astrogeology Science Center, Flagstaff, AZ, USA}
%\affiliation{3}{}
%\affiliation{4}{}
%\affiliation{5}{}

@@

\correspondingauthor{C. Marmo}{chiara.marmo@u-psud.fr}

@@

\begin{keypoints}
\item Inter-operable data formats 
\item 
\end{keypoints}
